A \texttt{shiny} New Opportunity for Interaction with Big Data in Undergraduate Education

### 2015-05-23 Body/ShinyDBSampler/ShinyDBSampler.Rnw
Fixing wrong order of barplot for values -2 and -1, also fix description in the results section

ggplot() +
  geom_bar(aes(x=as.character(value-3), weight=means,fill=polarity),data=qu.means,width=.5, position="dodge", size=I(2)) + 
  theme_bw() + scale_colour_brewer("", palette="Set1") + 
  scale_shape_manual("", values=c("-","+")) +
#  scale_shape_manual("", values=15:18) +
#  geom_point(aes(x=as.character(value-3), y=n,  colour=question.in.set, shape=polarity), data=qu.summary, size=I(7),position="dodge") +
  facet_grid(facets=.~set) + 
  xlab("Responses (Post Reverse-Scoring All Negative Item)") + ylab("Count") 
@

@@

The barcharts found in Figure \ref{fig:OverallSetBars} show that the distribution for each item set is heavily skewed to the left, with the majority of students having neutral to positive responses. The small bump at the far left of each distribution indicates that there was a small minority of students with expressedly negative views. The response distributions indicate that on average students found the Shiny Database Sampler easy to use, found that the tool connected them to sampling concepts and felt moderately engaged with the census data that was accessed with the application.

>>>>

ggplot() +
  geom_bar(aes(x=as.factor(value-3), weight=means,fill=polarity),data=qu.means,width=.5, position="dodge", size=I(2)) + 
  theme_bw() + scale_colour_brewer("", palette="Set1") + 
  scale_shape_manual("", values=c("-","+")) +
#  scale_shape_manual("", values=15:18) +
#  geom_point(aes(x=as.character(value-3), y=n,  colour=question.in.set, shape=polarity), data=qu.summary, size=I(7),position="dodge") +
  facet_grid(facets=.~set) + 
  xlab("Responses (Post Reverse-Scoring All Negative Item)") + ylab("Count") 
@

@@

The barcharts found in Figure \ref{fig:OverallSetBars} show that the distribution for each item set is heavily skewed to the left, with the majority of students having neutral to positive responses. The small tail to the left in each distribution indicates that there was a small minority of students with expressedly negative views. The response distributions indicate that on average students found the Shiny Database Sampler easy to use, found that the tool connected them to sampling concepts and felt moderately engaged with the census data that was accessed with the application.
